---
title: "HW2_Question1"
author: "Ethan M. Lotz"
date: "September 26, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
```

##Question 1

**In R, do the following:**

a.) Load the built-in dataset state.x77 into R's memory
```{r}
data(state)
head(state.x77)
```

b.) List the objects in your R session. Get help for the state object.
```{r}
ls.str()
```

c.) What type of object is state.x77?
```{r}
class(state.x77)
```

d.) Create a new object called new.state that is a data.frame based on the data stored in state.x77.
```{r}
new.state <- data.frame(state.x77)
```

e.) Attach the new.state object into the search path.
```{r}
attach(new.state)
```

f.) Compute the mean of the Illiteracy vector from the new.state object, and its residuals from the mean
value.
```{r}
mean(new.state$Illiteracy)
sd(new.state$Illiteracy)
```

g.) Print the elements of Illiteracy that are greater than the median illiteracy. Print the elements of
Murder that are greater than its median.
```{r}
new.state$Illiteracy[new.state$Illiteracy > median(new.state$Illiteracy)]
new.state$Murder[new.state$Murder > median(new.state$Murder)]
```

h.) Plot Illiteracy on the x-axis and Murder on the y-axis. From interacting with the graph, what 3 states
have the highest murder rates?
```{r}
plot(new.state$Illiteracy, new.state$Murder, xlab="State Illiteracy", ylab="Murder Rate")
```

i.) The plot function has an optional argument, type, that controls what type of plot is made (points,
lines, etc). In particular, type = ’n’ plots nothing, but sets up and draws axes and axis labels. Use this
to generate a scatterplot of Illiteracy and Murder, but with the state abbreviations labeling the points,
instead of the default plotting character.
```{r}
ggplot(new.state, aes(x=new.state$Illiteracy, y=new.state$Murder)) + geom_text(aes(label=state.abb),size=3)
```

j.) Write a function is.min that returns a logical vector identifying the minimum values. Write another
function (call it mins) that calls is.min and returns the numerical indices of the minimum values. Apply
mins to the Illiteracy vector.
```{r}
is.min <- function(a) a==min(a)
mins <- function(a) which(is.min(a))
mins(new.state$Illiteracy)
```

