---
title: "HW2_Q2"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(UsingR)
library(DT)
library(reshape)
library(ggplot2)
```

##Question 2

```{r}
data(crime)
```

Check the dimensions
```{r}
dim(crime)
```

Check classes of variables in rows and columns
```{r}
class(crime)
lapply(crime, class)
```

Check summary statistics for rows/columns
```{r}
summary(crime)
```

Display rows/columns as a table sortable by min/max value. In descending order by default.
```{r}
datatable(crime)
```

Visualized boxplots of rows/columns, where appropriate. Plot data on different scales on separate boxplots
```{r}
meltcrime <- melt(crime)
boxplot(data=meltcrime, value~variable)
p <- ggplot(meltcrime, aes(factor(variable), value)) 
p + geom_boxplot() + facet_wrap(~variable, scale="free")
```

Visualize data using histograms and/or density plots, if relevant
```{r}
hist(crime[,1], main=paste("Histogram of Crime in 1983"), xlab=paste("1983 Crime Rate"))
hist(crime[,2], main=paste("Histogram of Crime in 1993"), xlab=paste("1993 Crime Rate"))
```

Make any other dataset-specific plots, e.g., plotting one variable vs. the other, performing linear regression on it
```{r}
t.test(crime[,1],crime[,2],paired=TRUE)
```

Discussion:
The data set "crime" contains the violent crime rates for the 50 states in the year 1983 and a decade later in 1993. The summary statistics for the data set show the median crime rate in 1983 was 397.9 (IQR 245.4-553.0) and 535.5 (IQR 328.8-758.1). A paired t-test shows that country wide violent crime rate significantly increased between 1983 and 1993 (t=-7.68, p-value < 0.0001). It would be interesting to see how this data set compares with crime rates from both 2003 and 2013.
